A Switching Planner for Combined Task and Observation Planning

### 2010-11-25 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/dtpddl.tex
starting paragraphs

>>>>

From hereon, in order to simplify the discussion (and implementation)
we shall restrict our attention to POMDPs with deterministic
actions. It is worthwhile noting that any POMDP with stochastic
actions can be compiled into an equivalent deterministic-action POMDP,
where all the original action uncertainty is expressed in the
starting-state distribution~\cite{ng:Jordan:2000}. In our setting,
that of finite-horizon planning, such a compilation yields a finite
flat representation of the original POMDP, only with deterministic
actions.

### 2010-11-25 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
starting paragraphs

We now describe our continual planning approach that switches between
sequential and decision-theoretic planning sessions.

Sequential planning proceeds in a continual manner until the
verification of an assumption about runtime state is scheduled. At
that point the system switches to a decision-theoretic planner that is
used to tailor sensory processing by the robot to test the validity of
the assumptions made so far.

In this work, the problem at hand is a POMDP described in DTPDDL. From
hereon, we restrict our attention to POMDPs with deterministic
actions. Therefore it is worthwhile noting that any POMDP with
stochastic actions can be compiled into an equivalent
deterministic-action POMDP, where all the original action uncertainty
is expressed in the starting-state
distribution~\cite{ng:Jordan:2000}. In our setting, that of
finite-horizon planning, such a compilation yields a finite flat
representation of the original POMDP, only with deterministic
actions.

>>>>

We describe our continual planning approach that switches between
sequential and contingent sessions. Continual planning and execution
proceeds in a deterministic-action POMDP described in DTPDDL. During a
sequential session, planning is performed by a ``classical''
system,\footnote{That is, a system designed to solve fully observable
deterministic tasks.}  and execution proceeds according to the {\em
trace} computed by that system. Taking the form of a classical plan,
the {\em trace} specifies a sequence of POMDP actions that achieve the
agent's objectives in a deterministic approximation, i.e., {\em
determinisation}, of the problem at hand. More precisely, the trace is
an interleaved sequence of POMDP actions and {\em assumptive}
actions. The latter correspond to assumptions the planner makes about
the truth value of {\em runtime state variables} -- e.g. that a box of
cornflakes is located in the kitchen at the third plan step. Another
kind of assumption, called an {\em applicability} assumption, is made
when the trace includes an action $\action$ that is not applicable
with probability $1$ at the belief-state
\bstate\ that the system is projected to be in when \action\ is executed, 
i.e., $\exists\state\in\states
\bstate(\state) > 0$ and $\poss(\action)\not\subseteq\state$. By
scheduling
\action,  the serial planner makes an assumption about the
observability of the precondition $\poss(\action)$.

Our approach always begins with a sequential session. Non-assumptive
actions from the trace are executed until the applicability of the
next scheduled action, here \action, is questionable. A contingent
session then begins, which tailors sensory processing by the agent to
perceive whether the assumptions made in the trace hold. For each
active assumption in the trace, we add a {\em disconfirm} action to
the POMDP whose execution is rewarding (resp. costly) if the
assumption is false (resp. true). We also add one {\em confirm} action
that is rewarding (resp. costly) to execute if $\poss(\action)$ is
true (resp. false). If execution of the contingent plan applies a
disconfirm action, then a new sequential session begins at the current
underlying belief-state. If the confirm action is executed, the
sequential session is resumed, and \action\ is executed. Otherwise,
control rests in the continual session.
%%
Finally, because contingent planning is only practical in relatively
small POMDPs, contingent sessions proceed in an abstract decision
process determined by the current trace. That abstract process is
constructed by first omitting all variables from the model that are
not featured in the trace, and by then iteratively refining that
abstraction while the resulting model is of a practicable size.
